Parameter estimation

### 2023-03-08 SFE-article/Sections/Low_mach_number_expansion.tex
08.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

@@

>>>>

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

@@

		A general formulation the internal energy for a real gas is:

	{\footnotesize
		\begin{equation*}
			de=C_vdT-\left[P-T\left(\cfrac{\partial P}{\partial T}\right)_{v_m}\right]dv_m
	\end{equation*} }

	where $v_m$ is the molar volume.

	The internal energy is a function of two intensive properties, in this case $T$ and $V$. But, in the case of an ideal gas, the equation of state is such that the second term in this equation is identically equal to zero. So the ideal gas is a special case in which the molar internal energy is a function only of temperature. For Peng-Robinson equation of state, the internal energy is defined as

	{\footnotesize
	\begin{equation*}
		e = C_vT + \cfrac{a\left(\alpha -T\cfrac{d \alpha}{dT}\right)}{2\sqrt{2}b} \ln \left[ \cfrac{1+b\left(1-\sqrt{2}\rho\right) }{1+b\left(1+\sqrt{2}\rho\right)} \right]
	\end{equation*} }

	Assuming constant temperature and pressure along space and in time:

	{\footnotesize
		\begin{equation*}
			\lim_{\Delta T, \Delta P \rightarrow 0_+ } \rho A_f \left( \cfrac{\partial e }{\partial t} + V \cfrac{\partial e}{\partial z} \right) - \cfrac{\partial}{\partial z} \left( k \cfrac{\partial T}{\partial z} \right) + P_0 \cfrac{\partial A_f V}{\partial z} = 0 \rightarrow \cfrac{\partial A_f V}{\partial z} = 0
		\end{equation*}
	}

	It can be deduce that the continuity equation becomes $\frac{\partial \rho_f}{\partial t} = 0$ at constant temperature and pressure. Moreover, the incompressibility condition $div(A_fV)=0$ is obtained.

	Assuming an arbitrary function $\hat{P}$, which describe the total pressure, the dimensional momentum equation can be written as

	{\footnotesize
		\begin{equation*}
			V \underbrace{ \left( \cfrac{\partial \rho_f A_f}{\partial t} + \cfrac{\rho_f V A_f}{\partial z} \right) }_{Continuity~equation} + \rho_f A_f \cfrac{\partial V}{\partial t} + \rho_f V A_f \cfrac{\partial V}{\partial z} = - A_f \cfrac{\partial \hat{P}}{\partial z}
		\end{equation*}
	}

	From the incompressibility conditions we can deduce that

	{\footnotesize
		\begin{equation*}
			\cfrac{\partial A_f V}{\partial z} = 0 \rightarrow A_f \cfrac{\partial V}{\partial z} = - V \cfrac{\partial A_f}{\partial z}
		\end{equation*}
	}

	By combining both above equations, assuming that $\partial V / \partial t = 0$:

	{\footnotesize
		\begin{equation*}
			\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} = \cfrac{\partial \hat{P}}{\partial z} \rightarrow \int	\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int \cfrac{\partial\hat{P}}{\partial z} dz
		\end{equation*}
	}

	The l.h.s integral can be solved by assuming $\rho_f$ is constant and introducing $u=A_f V$

	{\footnotesize
		\begin{align*}
			& \int	\cfrac{\rho_f V^2}{A_f} \cfrac{\partial A_f}{\partial z} dz = \int	\cfrac{\rho_f V^2}{A_f} \cfrac{A_f^2}{A_f^2} \cfrac{\partial A_f}{\partial z} dz \\
			&= \rho_f u^2  \int \cfrac{1}{A_f^3} \cfrac{\partial A_f}{\partial z} dz = - \cfrac{\rho_f u^2}{2 \Delta A_f^2} = - \cfrac{\rho_f \Delta V^2}{2} \\
			& \int \cfrac{\partial \hat{P}}{\partial z} dz = \Delta \hat{P}
		\end{align*}
	}

	The final form of the momentum equation corresponds to the Bernoulli's principle

	{\footnotesize
		\begin{equation*}
			\Delta \hat{P} = - \cfrac{\rho_f \Delta V^2}{2} \xrightarrow[]{P_0 = \text{const}} \Delta M_a^2 P_1 = - \cfrac{\rho_f \Delta V^2}{2}
		\end{equation*}
	}

	The Bernoulli's principle can be used to find the hydrodynamic pressure caused by varying cross-section at steady-state. Moreover, if the flow velocity is relatively low and so all pressure changes are hydrodynamic (due to velocity motion) rather than thermodynamic. The effect of this is that $\partial \rho / \partial p = 0$. In other words, the small changes in pressure due to flow velocity changes do not change the density. This has a secondary effect -- the speed of sound in the fluid is $\partial p/\partial \rho = \infty$	in this instance. So there is an infinite speed of sound, which makes the equations elliptic in nature. It can be deduced that at the isothermal conditions the density in the system propagates with the same speed as pressure due to the fact that they are both connected through the equation of state.

### 2023-03-08 SFE-article/Sections/Model.tex
08.03

\documentclass[../Parameter_fitting.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

	\sout{The main components of the model are three one-dimensional differential equations related to mass balances (solid and fluid phase) and heat balance. As in all batch processes, our system has only one steady state. The steady-state occurs only if the solute is entirely taken out of the biomass.

		The extraction from a fixed bed is an unsteady process, implying that the solute concentrations in the solid and solvent phases vary over time and space. The convection and the diffusion of the mass and the heat are considered only in the axial direction. The radial distribution of such properties like a velocity is assumed to be flat in that direction. The assumption of the flat velocity profile allows considering a lack of back mixing. The pressure drop in the bed is assumed to be assumed to negligible. Under such conditions, the fluid flow can be considered a plug flow.

		Since the solute is assumed to be a single pseudo-component, there is only one mass balance equation for each phase (Eq.s \ref{Model_fluid} and \ref{Model_solid}). On the other hand, there is only one heat balance (Eq. \ref{Model_heat}) because the presence of a single pseudo-phase is assumed.

		Moreover, the process model does not consider the change of particle size or the void fraction during the process. The particles are assumed to be uniformly distributed along the bed and to have the same size.}

@@

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f \varepsilon (z) \right)}{\partial t} + \cfrac{\partial \left( \rho_f u \right)}{\partial z} = 0
			\label{EQ: Continuity}
		\end{equation}
	}

	where $u$ is the superficial velocity, $\varepsilon$ is the bed porosity and $\rho_f$ is the fluid density.

@@

			\begin{figure}[h!]
				\centering
				%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
				\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=1.0\linewidth]{Figures/SFE_draft.pdf}	
				\caption{The extraction mechanism}
				\label{fig: SFE_Mechanism}
			\end{figure}

>>>>

\documentclass[../Article_Model_Parameters.tex]{subfiles}
\graphicspath{{\subfix{../Figures/}}}
\begin{document}

@@

	{\footnotesize
		\begin{equation}
			\cfrac{\partial \left( \rho_f A_f \right)}{\partial t} + \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} = 0
			\label{EQ: Continuity}
		\end{equation}
	}

	Considering the mass flow-rate which is constant in time, the temporal derivative become zero and the spacial derivative can be integrated along $z$.

	{\footnotesize
		\begin{equation*}
			\int \cfrac{\partial \left( \rho_f v A_f \right)}{\partial z} dz = 0 \rightarrow F=\rho_f v A_f
		\end{equation*}
	}

	where $F$ is a constant obtained from the integration. The constant $F$ can be understood as the mass flux per unit area which is assumed to be constant along $z$. $F$ can treated as a control variable, which can change in time but it is constant in space. Such a assumption allows to find the velocity profile which satisfy the mass continuity based on $F, A_f$ and $\rho_f$. The fluid density $\rho_f$ density is connected through equation of state with thermodynamical pressure, which is assumed to be constant along $z$ (due to the low-Mach number) and temperature. The variation in density might be caused by the accumulation of the fluid in the system (which happen instantaneously along $z$) or by temperature change. To simplify the dynamic of the system, it is assumed that $F=F(t)$ is a control variable and affects the whole system instantaneously.

@@

			\begin{figure}[h!]
				\centering
				%	\includegraphics[trim  = 6cm 0cm 3cm 0cm,clip,width=\linewidth]{Figures/SFE_draft.png}
				\includegraphics[trim = 5.8cm 1.1cm 6cm 0.8cm,clip,width=\columnwidth]{Figures/SFE_draft.pdf}	
				\caption{The extraction mechanism}
				\label{fig: SFE_Mechanism}
			\end{figure}
